---
title: "Introduction to Binomial"
author: "Jameson Hohbein"
date: "May 3, 2019"
output: html_document
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial 

The binomial package is a resource that allows users to make binomials calculations along with many other features that allow users to expand their mathmatic knowledge. 

## Choosing a binomial 

This function calculates the number at which k successes can occur in n trials. 

```{r}
binc = bin_choose(n=5,k=2)
binc
```

## Probability of binomials

This function calculates the chances of getting a number of successes out out of a number of trials with a stipulated probability. 

```{r}
binprob = bin_probability(success=2,n=5,k=0.5)
binprob
```

## Binomial Distribution 

This function produces a list of the the chances of several successes up to the stipulated trial number under a stipulated probability. 

```{r}
bindis = bin_distribution(trials=5,prob=0.5)
bindis
```

You can then plot your distribution in a plot 

```{r}
plot(bindis)
```

## Cumulative Binomial 

This function produces a series like the distribution of the binomial but it also provides a cumulative count that keeps track of the total aggregated sums of the probabilities. 


```{r}
bincum = bin_cumulative(trials=5,prob=0.5)
bincum
```

You can also plot the distribution

```{r}
plot(bincum)
```

## Binomial Variable

This function creates a binvar object which will tell users what trials and probability they entered. 

```{r}
binvar = bin_variable(trials=10,prob=0.3)
```

You can print the binvar object by calling it. 

```{r}
binvar
```

You can summarize and print the binvar object like so

```{r}
binsum = summary(binvar)
binsum
```

## Measurements 

There are also several measurements you can use that provide the user resources. For instance, mean, variance, mode, skewness, and kurtosis of the binomial are all functions to be utilized. 
```{r}
bin_mean(10,0.3)

bin_variance(10,0.3)

bin_mode(10,0.3)

bin_skewness(10,0.3)

bin_kurtosis(10,0.3)
```
